A Bayesian Network Model-based decision support tool for sustainability in the Australian Winegrowing Industry.

### 2024-12-03 article.tex
revising introduction, start of methods revision.

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}

\title{A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.}

\author[1,2,3,*]{Bryce Boyd}
\author[1]{Kate Helmsteadt}
\author[2]{Mardi Longbottom}
\author[1]{Kerrie Mengersen}

\affil[1]{QUT, Mathematical Sciences, Brisbane, Australia}
\affil[2]{AWRI, Adelaide, Australia}
\affil[3]{Food Agility CRC}

\affil[*]{bryce.polley@awri.com.au}

@@

\begin{abstract}
Sustainability in the Australian winegrowing industry involves complex, interacting factors. To address this, we developed a Bayesian Network model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes. The Bayesian Network model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability. A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use. This study underscores the potential of Bayesian Networks as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
\end{abstract}
\begin{document}

@@

\section*{Introduction}
The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~(\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}). This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~(\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}). This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model for Australian. This broad model was followed by a more specific case study looking at the Coonawarra winegrowing region. Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~(\cite{beaumelleBiodiversityConservationEcosystem2023}) criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics~(\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023, wayeCarbonFootprintsFood2008}). In this study we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.

BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~(\cite{korbBayesianArtificialIntelligence2011}). Bayesian Networks (BNs) also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiments, outcomes from published literature, and so on. In this study, the BNs integrated expert knowledge and region-specific data within a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing. This methodology shed light on current sustainability practices, identified critical areas for intervention and facilitated evolution of the potential impact of various management action or climate scenarios.

This research is guided by several fundamental inquiries aimed at enhancing our understanding of sustainability in viticulture. A primary question is how key factors impact the environment, and how these factors can be rigorously defined and quantified. Furthermore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra region to illustrate how the relative influence of factors change. Additionally, the study investigates how these factors interact with each other. The final question is, how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

An industry panel comprising experts in viticulture and sustainability, was convened to guide the project. The panel acted as a catalyst in the early stages of the research to help explore the above questions. The panel input was supported by a comprehensive literature review, which established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing. To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods were employed in its creation via expert consultations and data analysis. The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.

@@

In agriculture, the consideration of environment is critical to the success of the industry. The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change~(\cite{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}). The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry~(\cite{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}). It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined~(\cite{santiago-brownSustainabilityAssessmentWineGrape2015}).

Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes~(\cite{dichiaraCollaborativeApproachAchieving2024}). In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers~(\cite{dumbrellComparingAustralianPublic2024}). While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}).
% old comment
% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review. G, K and F seem quite relevant but this paragraph doesnt do them justice so expand or move.
% 
% Review further comments about this paragraph - its not a good piece of work but it is important to consider how impact and sustainability is or could be measured and interpretted. Perhaps go deeper like you did in your confirmation.
Methods for measuring sustainability comprise a wide variety that of approaches with the use of index systems being common. The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions. As~\cite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment~(\cite{floresWhatSustainabilityWine2018}). The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes~(\cite{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}). For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators)~(\cite{klemes_assessing_2015}). This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes. By focusing on key indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision. These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, thereby enabling more targeted and effective sustainability efforts. Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End suggestion.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Literature Review}

The literature review was designed to assess existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions. These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification. The most prominent way of informing the model was the construction of an initial straw-man model to describe different relationships explored in the literature, which helped as a beginning point for the experts to discuss the specific applicability of relationships for different Australian contexts. The literature review was done using systematic search of terms, broadly based on key factors given from the industry panel, was conducted. The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:

@@

Specific inclusion and exclusion criteria were applied in the literature search. Articles were only excluded if they were not available in full text or were not written in English. In-depth reviews of sustainability within agriculture or winegrowing and methodological reviews within this context were also included.

@@

The expert panel comprising specialists in viticulture and sustainability was engaged throughout the literature review process. The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
% By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture. This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.

@@

A BN is a graphical model, comprising of nodes and edges. Uniquely, Bayesian Networks contain the network's operations within the nodes themselves instead of across the edges. In the BN structure adopted in the study, these operations were encapsulated through a conditional probability table for each node, with connections between the nodes being defined by edges. This results in computational simplicity, since each node is dependent only on its parent and simplicity within the calculations are achieved through sum, multiplication and division operations
% . However, great complexity is introduced when a node is informed by many parents, which can also have many parents themselves. The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes 
(\cite{korbBayesianArtificialIntelligence2011}).
% The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.

The use of a BN allowed for collaboration between experts to create a causal structure, identifying important factors and agreeing on the relationships between factors
%. The ability to include perspectives from industry experts and create a causal structure. The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact 
(\cite{pourretBayesianNetworksPractical2008}). Furthermore, data collected across Australia could also be used to help inform the model structure as well as quantify the associated conditional probabilities alongside expert opinion.

@@

% Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}. Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes. Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes. This is an iterative application of~\ref{bayesformula}, which can be achieved through

Given the directed acyclic graph (DAG) structure of the BN, each quantification of a node only depends on the parent of that node, and is conditionally independent of the other nodes in the network collectively, then,

@@

The ability to present different probable outcomes for various sets of events and their associated uncertainties enables the conduction of inference. This inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present. The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods. One of the greatest abilities of this type of inference is Marginalization. In which, the outcome of a particular event can be determined irrespective of other outcomes. This type of marginalisation is intuitively represented as nodes conditional independence and illustrated inherently through the structure of the graph by its edges. Bayesian Networks created in this study were created using BayesFusion~(\cite{bayesfusionGeNIeModelerUSER2022}) to calculate the networks and their probabilities. 
% The Bayes fuse software was used both through the GUI interface and the SMILE API \cite{bayesfusionGeNIeModelerUSER2022} system using C++ (\cite{ISO:2012:III}).

@@

The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}). The process progressed iteratively through problem definition, structure, parameterisation, and validation. Initially, experts were informed about the process to ensure a clear understanding of each step and to highlight common pitfalls, as well as how these would be addressed. Some of the common problems identified by both authors include a lack of understanding of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates. To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope. Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency. Communication included in-person and electronic one-on-ones and group sessions; with elicited of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.

Each workshop had a primary focus such as: scope, structure or parameterisation; with, prior concepts being built upon iteratively. The first important establishment was the scope of the network, and how well it could or couldn't be adapted to a wide variety of circumstances within the Australian winegrowing industry. Following this was the discussion around the structure of the network, which entailed the description of relationships and stricter definitions of each factor to one another. Finally, variables were paramatised using conditional probabilities.

To introduce new concepts and how they interacted, preliminary simplified versions (straw-man examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon. The use of these straw-man examples enabled a more engaged and effective review process. Experts were initially able to interact with elements of the model and see how they worked together. The straw-man examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.

@@

As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network (\cite{korbBayesianArtificialIntelligence2011}). For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes. The classes represented a positive or negative contribution to a vineyard's environmental outcome helping to reduce this complexity. Furthermore, the intricacy of variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard. To attempt to capture this complexity but not dilute the ability to work with various scenarios experts were asked to provide key input into complex CPT cells and the CPT cells were interpolated. The experts then reviewed and amended or approved the derived CPTs.

This interpolation method utilised filling in cells between two anchored points. One point represented the case of all factors being true/positive and the other represented all factors being false/negative. The interpolation was achieved by designating each factor an attributed weight, where weights were indicative of a factor's overall influence to its child node. During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.

Using this method, a given probability was calculated using
\begin{equation}
        p=x\sum_{i}^{n}\alpha_{i} + y\sum_{i}^{m}\beta_{i} 
\end{equation},
n count of true (or ideal states) and m false (or not ideal states) factors. The solutions for when all contributing factors are true ($p_t$) or all are false ($p_f$) is,
\begin{equation}
        p_t=x\sum_{i}^{n}\alpha_{i} 
        \text{ and }
        p_f=y\sum_{i}^{m}\beta_{i}
\end{equation}.
The values for $x$ and $y$ can be derived using the sum of the provided BN weights. An assumption of `smoothness' is taken between worst and best case scenarios when utilising this method. All possible combinations between all states being true (or ideal) and all being false (not ideal) are also mirrored such, with the only consideration being given, is that of how heavily weighted a variables state is compared to the others.

@@

The method for validation sought to address criteria presented by~\cite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity. Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature. Face validity involves evaluating whether the model appears to be a valid representation based on expert judgment. Content validity checks that the model includes all relevant factors and relationships from both literature and expert knowledge, ensuring nothing critical is omitted. Concurrent validity is concerned with whether the BN or its components behave consistently when compared with other similar networks. Convergent validity assesses how closely the BN aligns with models that describe similar systems, while discriminant validity ensures that the BN is distinct from models representing different systems. Finally, predictive validity examines the BN's ability to accurately predict system behavior.Validation steps were partly incorporated during the process of constructing the Bayesian network itself. When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario. The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices. Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}).

The face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases. This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations. This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors~(\cite{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}).
% Specifically, the question of water resources, which was central to the model and highly interrelated \cite{carmonaUseParticipatoryObjectOriented2011}.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{biblatex}

\addbibresource{references.bib}

\title{A Bayesian Network Model-based decision support tool for sustainability in the Australian Winegrowing Industry.}

\begin{document}

% \author[1,2,3,*]{Bryce Boyd}
% \author[1]{Kate Helmsteadt}
% \author[2]{Mardi Longbottom}
% \author[1]{Kerrie Mengersen}

% \affil[1]{QUT, Mathematical Sciences, Brisbane, Australia}
% \affil[2]{AWRI, Adelaide, Australia}
% \affil[3]{Food Agility CRC}

% \affil[*]{bryce.polley@awri.com.au}

@@

\begin{abstract}
Sustainability in the Australian winegrowing industry involves complex, interacting factors. To address this, we developed a Bayesian Network model, integrating data and expert input to summarise key factors, their relationships, and their impacts on vineyard outcomes. The Bayesian Network model was iteratively refined, utilising variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability. A case study of the Coonawarra and Riverland regions was conducted to highlight regional differences whilst emphasising industry-wide concerns, such as agrochemical use and water consumption. This study underscores the potential of Bayesian Networks as powerful tools for sustainability analysis in agriculture to connect industry concerns, analyses and literature, offering valuable insights for sustainable vineyard management.
\end{abstract}

@@

\section*{Introduction}
The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~(\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}). This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~(\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}). Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~(\cite{beaumelleBiodiversityConservationEcosystem2023}), the criterion for assessing sustainability has become multifaceted, leading to the creation of many institutions with varying industry-specific approaches to creating sustainability metrics~(\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023, wayeCarbonFootprintsFood2008}). Whilst various sustainability frameworks exist, they are often limited in scope, failing to adapt to regional differences and requirements, and to capture the complex, interconnected nature of factors~\cite{santiniSustainabilityWineIndustry2013, christ2013critical}. Existing tools frequently focus on single metrics and relationships and cannot integrate regional variability or address the unique environmental challenges of Australian winegrowing~(\cite{baianoOverviewSustainabilityWine2021,leask2019sustainable, abbalDecisionSupportSystem2016}).

As the agricultural industry in Australia continues to be affected by international market demands, disease pressures, natural disasters and social change; the question of sustainability has continued to grow in importance ~(\cite{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}). The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry~(\cite{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}). It is essential to consider each factor concerning these perspectives, and to be explicit in how they are defined~(\cite{santiago-brownSustainabilityAssessmentWineGrape2015}).

This study investigates sustainable practices in Australian winegrowing using Bayesian Networks (BNs), using a broad model for Australia to structure the connections between industry concerns. Collaboration between experts from different perspectives helps to reconcile opinions regarding other factors and their contribution to sustainable outcomes~(\cite{dichiaraCollaborativeApproachAchieving2024}). In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers~(\cite{dumbrellComparingAustralianPublic2024}). While there is a general agreement on broader regulatory needs, the industry requirements vary significantly between different wine regions due to climate, soil types and water resources~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}). To address this Regional-specific models were subsequently derived from this network's structure, adding conditional probabilities to compare different industry priorities between regions and to delve deeper into the intensity of connections between industry concerns by reflecting the strength of these relationships through a probabilistic network.

BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems. BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiments, outcomes from published literature, and so on~(\cite{korbBayesianArtificialIntelligence2011}). We have chosen to use BNs due to their adaptability to address regional concerns and model-specific scenarios, as well as because of their wide use in agricultural applications~\cite{abbalDecisionSupportSystem2016, carmonaUseParticipatoryObjectOriented2011, luDiseaseRiskForecasting2020, barton2008bayesian, cain2001planning}. In this study, we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node (node definitions are detailed in the results) within the network, linking relevant factors through structures described by an expert panel. Specialist knowledge and region-specific data were integrated into the BN within a structured framework to quantify the impacts of various factors on sustainability. This methodology shedding light on current sustainable practices, identifying critical areas for intervention and facilitating the creation of metrics to assess the evolution and impact of various management actions and climate scenarios.

Several fundamental inquiries guided this research to enhance our understanding of sustainability in viticulture. The primary driving question being, how key factors impact the environment and how these factors can be rigorously defined and quantified. Furthermore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra and Riverland regions to illustrate how the relative influence of factors changes. Additionally, the study investigates how these factors interact with each other. The final question is how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge. To address these objectives, an industry panel of viticulturists and sustainability experts provided critical input supported by an extensive literature review. To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods was employed in its creation via expert consultations and data analysis. The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.

@@

Given the complexity of factors influencing sustainability, the adopted approach integrates a comprehensive literature review with expert elicitation and BN. The literature review was designed to identify key factors and their interactions, informed by insights from an expert panel specialising in viticulture and sustainability. Bayesian Networks were chosen to complement this as the primary modelling tool due to their ability to describe these relationships in a causal fashion and capture them probabilistically.

The expert panel guided the selection of regions as case studies, recommending regions that leveraged their specialised knowledge and favoured available data. The following subsections detail the literature review process, the construction and quantification of Bayesian Networks, and the validation and sensitivity analyses conducted to ensure robustness.

\subsection*{Literature Review}

The literature review was designed to assess existing knowledge on sustainability in viticulture to identify key factors influencing sustainability and understanding their interactions. The literature review was conducted using a systematic search of terms, based on key factors from the industry panel. The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:

@@

Specific inclusion and exclusion criteria were applied in the literature search. Articles were only excluded if they were not available in full text or were not written in English. In-depth sustainability reviews within agriculture or winegrowing and methodological reviews within this context were also included.

@@

The expert panel comprising specialists in viticulture and sustainability was engaged throughout the literature review process. The panel guided the selection of relevant articles and helped refine the inclusion criteria through their list of critical factors.
% By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture. This approach ensured that the study's results were robust and scientifically sound and practically relevant and actionable for industry stakeholders.

@@

% old comment
% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this part out and absorb refs into the lit review. G, K and F seem quite relevant, but this paragraph doesn't do them justice, so expand or move.
% 
% Review further comments about this paragraph - it's not a good piece of work, but it is essential to consider how impact and sustainability are or could be measured and interpreted. Perhaps go deeper like you did in your confirmation.
% THIS IS WHERE KERRIES RESEARCGH GOOOEOEEESSSS
Methods for measuring sustainability comprise a wide variety of approaches, with index systems being common. Index systems are beneficial in comparing sustainability performance across different industries or geographic regions. As~\cite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating more straightforward interpretation and comparison.
Other approaches utilise identifying key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment~(\cite{floresWhatSustainabilityWine2018}). The measuring of sustainability can help to manage risk and promote resilience for industries through identifying sustainable goals and critical factors of interest that contribute to positive outcomes~(\cite{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}). For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators)~(\cite{klemes_assessing_2015}). This structure allows for a more granular sustainability assessment by linking broad guidelines to specific, measurable outcomes. By focusing on critical indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision. These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, enabling more targeted and effective sustainability efforts. Within this study, we focus on measuring key factors and establishing how they interact and ultimately affect the surrounding environment; the chosen method for this study is a Bayesian Network.
%  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End suggestion.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A BN is a graphical model comprising nodes and edges. Uniquely, Bayesian Networks contain the network's operations within the nodes instead of across the edges. In the BN structure adopted in the study, these operations were encapsulated through a conditional probability table for each node, with connections between the nodes defined by edges. This results in computational simplicity since each node is dependent only on its parent and simplicity within the calculations is achieved through sum, multiplication and division operations
% . However, great complexity is introduced when a node is informed by many parents, which can also have many parents themselves. The change in a single parent node affects all children of the network, often resulting in intractable systems, especially when nodes may have numerous classes 
(\cite{korbBayesianArtificialIntelligence2011}).
% The strength of this complexity over simple operations is the ability to encapsulate incredibly complex systems with simple definitions.

The use of a BN allowed for collaboration between experts to create a causal structure, identifying important factors and agreeing on the relationships between factors
%. The ability to include perspectives from industry experts and create a causal structure. The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another;and ultimately ,a factor's relation, direct or indirect, to a vineyard's environmental impact 
(\cite{pourretBayesianNetworksPractical2008}). Furthermore, data collected across Australia could also be used to help inform the model structure and quantify the associated conditional probabilities alongside expert opinion.

@@

% Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}. Within a Bayesian Network, an event can be considered any given node, and its outcome is one of the node's classes. Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes. This is an iterative application of~\ref{bayesformula}, which can be achieved through

Given the directed acyclic graph (DAG) structure of the BN, each quantification of a node only depends on the parent of that node and is conditionally independent of the other nodes in the network collectively; then,

@@

The ability to present different probable outcomes for various sets of events and their associated uncertainties enables the conduction of inference. This inference shows the difference between the likelihood of multiple outcomes with and without different evidence of prior nodes outcomes being present. The sets of different outcomes are then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods. One of the most remarkable abilities of this type of inference is Marginalization. The outcome of a particular event can be determined irrespective of other outcomes. This type of marginalisation is intuitively represented as nodes' conditional independence and illustrated inherently through the graph's structure by its edges. Bayesian Networks in this study were created using BayesFusion~(\cite{bayesfusionGeNIeModelerUSER2022}) to calculate the networks and their probabilities. 
% The Bayes fuse software was used both through the GUI interface and the SMILE API \cite{bayesfusionGeNIeModelerUSER2022} system using C++ (\cite{ISO:2012:III}).

@@

The Bayesian Network was constructed using data and expert elicitation, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}). The process progressed iteratively through problem definition, structure, parameterisation, and validation. Initially, experts were informed about the process to ensure a clear understanding of each step and highlight common pitfalls and how these would be addressed. Some common problems identified by both authors include a lack of knowledge of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates. To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope. Open communication was maintained during the entire process to help answer questions regarding the model and process and to maintain transparency. Communication included in-person and electronic one-on-ones and group sessions;,with elicited oxpert knowledge being primarily conducted through a series of workshops with the panel of industry experts.

Each workshop had a primary focus, such as scope, structure or parameterisation, with prior concepts being built upon iteratively. The first critical establishment was the scope of the network and how well it could or couldn't be adapted to a wide variety of circumstances within the Australian winegrowing industry. Following this was the discussion around the network structure, which entailed the description of relationships and stricter definitions of each factor to one another. Finally, variables were parameterised using conditional probabilities.

To introduce new concepts and how they interacted, preliminary simplified versions (straw-man examples) were provided to experts, with the intention that these examples be examined, critiqued, and improved upon. Findings from the literature review were combined with data from Sustainable Winegrowing Australia to derive these initial straw-man models, which helped as a beginning point for the experts to discuss the specific applicability of relationships and significance of factors withinthe Australian context. Using these straw-man examples enabled a more engaged and effective review process. Experts were initially able to interact with model elements and see how they worked together. The straw-man examples were crafted from a foundation of literature and data to offer a basic layman's understanding of critical factors and concepts, serving as a starting point for further development and discussion.

@@

As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network (\cite{korbBayesianArtificialIntelligence2011}). For comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes. The classes represented a positive or negative contribution to a vineyard's environmental outcome, helping to reduce this complexity. Furthermore, the intricacy of variables, particularly water use, was overwhelmingly interrelated to operations across the vineyard. To attempt to capture this complexity but not dilute the ability to work with various scenarios, experts were asked to provide critical input into complex CPT cells, and the CPT cells were interpolated. The experts then reviewed and amended or approved the derived CPTs.

This interpolation method utilised filling in cells between two anchored points. One point represented the case of all factors being true/positive, and the other represented all being false/negative. The interpolation was achieved by designating each factor an attributed weight, where weights indicated a factor's overall influence on its child node. During the workshop discussion, participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.

Using this method, a given probability was calculated using
\begin{equation}
        p=x\sum_{i}^{n}\alpha_{i} + y\sum_{i}^{m}\beta_{i} 
\end{equation},
n count of true (or ideal states) and m false (or not ideal states) factors. The solutions for when all contributing factors are true ($p_t$) or all are false ($p_f$) is,
\begin{equation}
        p_t=x\sum_{i}^{n}\alpha_{i} 
        \text{ and }
        p_f=y\sum_{i}^{m}\beta_{i}
\end{equation}.
The values for $x$ and $y$ can be derived using the sum of the provided BN weights. An assumption of `smoothness' is taken between worst and best-case scenarios when utilising this method. All possible combinations between all states being accurate (or ideal) and all being false (not ideal) are also mirrored, with the only consideration being given, is that of how heavily weighted a variable state is compared to the others.

@@

The validation method sought to address criteria presented by~\cite{pitchforthProposedValidationFramework2013}, who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity. Nomological validity ensures that the BN fits within a broader theoretical context, aligning with established literature. Face validity involves evaluating whether the model appears to be a valid representation based on expert judgment. Content validity checks that the model includes all relevant factors and relationships from literature and specialist knowledge, ensuring nothing critical is omitted. Concurrent validity concerns whether the BN or its components behave consistently when compared with similar networks. Convergent validity assesses how closely the BN aligns with models that describe identical systems, while discriminant validity ensures that the BN is distinct from models representing different systems. Finally, predictive validity examines the BN's ability to predict system behavior accurately.Validation steps were partly incorporated while constructing the Bayesian network itself. When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region or scenario. The selection process for experts encouraged diversity in their regional knowledge and expertise itobroaden their ability to critique choices. Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}).

The face and content validity of the network were questioned directly by the expert panel through the structure and conditional probability phases. This helped avoid some overtly specific scenarios in favour of broader vineyard decisions whilst allowing the model to address these behaviours in the future by targeting a region and incorporating its considerations. This approach went hand in hand with the content validation, where it was found additional nodes needed to be added to the general model to reflect important regional factors~(\cite{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}).
% Specifically, the question of water resources was central to the model and highly interrelated \cite{carmonaUseParticipatoryObjectOriented2011}.

Similarly, the convergent validity of the model was accomplished by checking the alignment of the model to other research, which helped to answer questions of concurrent validation further. This process was undertaken after the regional models were developed in unison with the literature review and creation of the Leximancer concept map. It was found that other studies emphasised the same variables selected by our experts. This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes~(\cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}). Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively~(\cite{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}).
